`flippant` --- An `R` package for the automated analysis of fluorescense--based

### 2016-09-11 inst/manuscript/manuscript.rmd
Reformat and ammend the abstract to follow BMC Bioinformatic's requirements;

# Abstract
The lipid scrambling activity of protein extracts and purified scramblases is
typically measured using a fluorescence--based assay. While the assay has
yielded insight into the scramblase activity in crude membrane preparations,
functional validation of candidate scramblases, stoichiometry of scramblase 
complexes as well as ATP--dependence of flippases, data analysis in its context 
has remained a task involving many manual steps. With the extension package 
`flippant` to `R`, a free software environment for statistical computing and 
graphics, we introduce an integrated solution for the analysis and 
publication--grade graphical presentation of dithionite scramblase assays and 
demonstrate its utility in revisiting an originally manual analysis from the 
publication record, closely reproducing the reported results.

>>>>

# Abstract
**Background:** The lipid scrambling activity of protein extracts and purified
scramblases is typically measured using a fluorescence--based assay. While the
assay has yielded insight into the scramblase activity in crude membrane
preparations, functional validation of candidate scramblases, stoichiometry of
scramblase complexes as well as ATP--dependence of flippases, data analysis in
its context has remained a task involving many manual steps.

**Results:** With the extension package `flippant` to `R`, a free software
environment for statistical computing and graphics, we introduce an integrated
solution for the analysis and publication--grade graphical presentation of
dithionite scramblase assays and demonstrate its utility in revisiting an
originally manual analysis from the publication record, closely reproducing the
reported results.

**Conclusions:**  `flippant` allows for quick, reproducible data analysis of
scramblase activity assays and provides a platform for review, dissemination and
extension of the strategies it employs.
